---
title: "adv_lab_1"
output: html_document
date: "2023-10-30"
---

## Loading Packages

```{r setup}
library(ggplot2)
library(sf)
library(tidyverse)
```

## Loading Boulder Data

```{r}
boulder <- st_read("D:/EAS648/lab_1/boulder_data/BoulderSocialMedia.shp")

boulder
```

## Exploring whether photos were taken near natural landmarks

In this part, I plan to explore whether most of the photos were taken near the landmarks, meaning that their NatMrk_Dis value is 0 or near 0. I also added Elevation and Social Media platform as variables, to explore trends in multiple data variables.

```{r}
boulder %>%
  filter(DB ==  'Pano' | DB == 'Flickr') %>%
  ggplot(aes(x = PT_Elev, y = NatMrk_Dis, color = DB)) +
  geom_point(alpha = .3) +
  labs(color = "Social Media")+
  xlab("Elevation (m)") +
  ylab("Distance to Natural Landmarks (m)")
```

In the result picture, we can notice that there is **a line that is parallel to x axis**, meaning that there are certain amount of images were taken at the natrual landmarks, but not most of them. We can also find out that most of the pictures were taken under 2200m. For different social media platforms, we can see that Flickr's pictures are more than the other platform. At the same time, pictures from Flickr are more concentrated, most of them were taken under 1900m, but pictures from Pano are more divergent.

## Exploring whether distribution of photos taken

In this part, I plan to explore the geographical distribution of photos. At the same time, I added variables of different social media to observe the distribution of pictures on different social media.

### Changing Projection and Select Data from Two Social Medias

```{r}
boulder = st_transform(boulder, 26753) 

boulder_social_media = boulder %>% filter(DB ==  'Pano' | DB == 'Flickr')

```

### Data Visualization
```{r}
ggplot() +
    geom_sf(data =boulder_social_media, aes(color = DB),
    fill = NA, alpha = .3) +
  labs(color = "Social Media") +
  xlab("Longitude")+
  ylab("Latitude")
```


From the picture we can see that most of the pictures **were taken north of 39.98 degrees north latitude**, while many pictures are **clustered near 40 degrees north latitude**. There is no direct connection between the different social media and the location of the pictures.